---
title: "Incarceration Data Analysis"
author: "Miranda Ma"
date: "11/20/2020"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
library("knitr")
```

## Introduction + Summary Information

I am focusing on Asian American and Pacific Islander (aapi) jail incarceration population and population rate. This analysis is based on the incarceration trends dataset provided by Vera Institute of Justice. 

From working with the dataset, average value of aapi jail population rate across all the counties in 2018 is `r mean_aapi_jail_rate_2018`, while that of 2008 is `r mean_aapi_jail_rate_2008`. The trend of average value of aapi jail population rate across all the counties from 2008 to 2018 is shown below. 

```{r trend_mean_aapi_jail_rate, echo=FALSE}
show(trend_mean_aapi_jail_rate)
```

The location(s) of the highest value of aapi jail incarceration rate was recorded in 2018 was `r highest_aapi_jail_rate$county_name`, `r highest_aapi_jail_rate$state` was a number of `r highest_aapi_jail_rate$aapi_jail_pop_rate`. The location(s) of highest value of aapi jail incarceration population in 2018 was `r highest_aapi_jail_pop$county_name`, `r highest_aapi_jail_pop$state` with the number of `r highest_aapi_jail_pop$aapi_jail_pop`. 

## Trends over time Chart
The trends I chose to explore here is the average jail incarceration rate for aapi across all counties from 2008 to 2018. I wanted to explore this to see the trend of this variable and it has a downward slope over the years. 

```{r, echo=FALSE}
trends_chart
```

## Variable Comparison Chart
The variables I chose to explore is aapi jail incarceration population and total jail population. From the chart, we can see that there is a somewhat positive relationship between the two variables in that when total jail incarceration population increases, aapi jail incarceration population also increases. 

```{r, echo=FALSE}
comparison_chart
```

## Map
This map is one that shows aapi jail incarceration rate (per 100,000 people). From this map we can see that most counties has a rate closer to 0, which can indicate two things: that the number of aapi incarcerated people is extremely low, or that the percentage of aapi in that region is very low. 

```{r, echo=FALSE}
map
```

